---
title: "Research on Treamill Scheduler"
output: html_notebook
author: Ce Gao
organization: Shanghai Jiao Tong University
---

Powered by R Notebook

## Idea

* Support policy
* Support multi-thread, at least. Or concurrent scheduler as omega

## Perior state-of-the-art implemenetation

The architecture of scheduler is simple, which has two strategies: spread and pack.

In the spread mode, the scheduler will select a new node to run the app. And spread mode is the default mode in treadmill.

In the pack mode, the scheduler will select the same node until the node has no capacity.

```{python, eval=FALSE, include=FALSE}
class SpreadStrategy(Strategy):
    """Spread strategy will suggest new node for each subsequent placement."""
    __slots__ = (
        'current_idx',
        'node',
    )

    def __init__(self, node):
        self.current_idx = 0
        self.node = node

    def suggested_node(self):
        """Suggest next node from the cycle."""
        for _ in range(0, len(self.node.children)):
            if self.current_idx == len(self.node.children):
                self.current_idx = 0

            current = self.node.children[self.current_idx]
            self.current_idx += 1
            if current:
                return current
        # Not a single non-none node.
        return None

    def next_node(self):
        """Suggest next node from the cycle."""
        return self.suggested_node()


class PackStrategy(Strategy):
    """Pack strategy will suggest same node until it is full."""
    __slots__ = (
        'current_idx',
        'node',
    )

    def __init__(self, node):
        self.current_idx = 0
        self.node = node

    def suggested_node(self):
        """Suggest same node as previous placement."""
        for _ in range(0, len(self.node.children)):
            if self.current_idx == len(self.node.children):
                self.current_idx = 0
            node = self.node.children[self.current_idx]
            if node:
                return node

        return None

    def next_node(self):
        """Suggest next node from the cycle."""
        self.current_idx += 1
        return self.suggested_node()
```

## Evualuation

There are two ways to evaluate the scheduler: evaluate the performance and the result. To evaluate performance, there is a benchmark, which could run the scheduler and schedule some virtual apps in virtual nodes. And we could get the response time and function calls graph.

As for the result, This research reuses the simulator in sparrow, which implements some state-of-the-art scheduling policies and simulate those policies in virtual environment. This research will introduce Morgan Stanley's trace data into the simulator and try to find which policy fits well.

#### Schedle apps in 500 nodes

There may be some errors during this evaluation, because the kernel switches the thread from core 8 to core 4 sometimes.

The time complexity is $$O(N_{app}^2)$$, but the benckmark counts the data preparation time into the total time, so the actual time coplexity should be $$O(N_{app})$$, and the accurate complexity should be $$O(N_{app} * \log N_{node})$$. In this evaulation, The number of nodes is a constant value, so it should be linear.

```{r Schedule apps in 500 nodes, echo=FALSE, message=FALSE, warning=FALSE}
library(plotly)

dt <- read.table("./500-node-from-500-to-1000-app/500-node-from-500-to-1000-app.txt",
                 col.names=c("number", "time"),
                 fill=FALSE,
                 strip.white=TRUE)

l1 = lm(data = dt, time ~ number)
l2 = lm(data = dt, time ~ I(number^2))

p <- plot_ly(data = dt, x = ~number, y = ~time, name = 'raw data', type = 'scatter') %>% 
  add_trace(y = predict(l2), mode = 'lines', name = 'X^2')

p
```

After edit:

```{r, echo=FALSE, message=FALSE, warning=FALSE}
library(plotly)

dt <- read.table("500-node-from-500-to-1000-app/500-node-from-500-to-1000-app-linear.txt",
                 col.names=c("number", "time"),
                 fill=FALSE,
                 strip.white=TRUE)

l1 = lm(data = dt, time ~ number)
l2 = lm(data = dt, time ~ I(number^2))

p <- plot_ly(data = dt, x = ~number, y = ~time, name = 'raw data', type = 'scatter') %>% 
  add_trace(y = predict(l1), mode = 'lines', name = 'linear')

p

```
